---
output: github_document
title: "slowraker"
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

> A slow version of the Rapid Automatic Keyword Extraction (RAKE) algorithm

[![Linux Build Status](https://travis-ci.org/crew102/slowraker.svg?branch=master)](https://travis-ci.org/crew102/slowraker) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/2ycx1m182va333ye?svg=true)](https://ci.appveyor.com/project/crew102/slowraker)

## Installation

You can get the stable version from CRAN:

```r
install.packages("slowraker")
```

Or the development version from GitHub:

```r
if (!require(devtools)) install.packages("devtools")

devtools::install_github("crew102/slowraker")
```

## Basic usage

There is one main function in the `slowraker` package - `slowrake()`. `slowrake()` extracts keywords from a vector of documents using the RAKE algorithm. This algorithm doesn't require any training data, so it's super easy to use:

```{r, eval = FALSE}
library(slowraker)

data("dog_pubs")
rakelist <- slowrake(txt = dog_pubs$abstract[1:5])
```

```{r, eval = TRUE, results = 'hide', echo = FALSE}
# Note, we have to split the README.Rmd up like this so that it doesn't print 
# the progress bar.
library(slowraker)
options(width = 100, digits = 2)

data("dog_pubs")
rakelist <- slowrake(txt = dog_pubs$abstract[1:5])
```

`slowrake()` outputs a list of data frames. Each data frame contains the keywords that were extracted for an element of `txt`:

```{r}
rakelist
```

You can bind these data frames together using `rbind_rakelist()`:

```{r}
rakedf <- rbind_rakelist(rakelist = rakelist, doc_id = dog_pubs$doi[1:5])
head(rakedf, 5)
```

## Learning more

* To learn about how the RAKE algorithm works as well as the basics of `slowrake()`, check out the "Getting started" vignette (`vignette("getting-started")`). Frequently asked questions are answered in the FAQs vignette (`vignette("faqs")`).
* All documentation is also on the package's [website](https://crew102.github.io/slowraker/index.html)