---
output: github_document
title: "slowraker"
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

> A slow version of the Rapid Automatic Keyword Extraction (RAKE) algorithm

[![Linux Build Status](https://travis-ci.org/crew102/slowraker.svg?branch=master)](https://travis-ci.org/crew102/slowraker) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/2ycx1m182va333ye?svg=true)](https://ci.appveyor.com/project/crew102/slowraker)

## Installation

```r
if (!("devtools" %in% installed.packages()[,1]))
  install.packages("devtools")

devtools::install_github("crew102/slowraker")
```

## Basic usage

There is one main function in the `slowraker` package, `slowrake()`. `slowrake()` will extract keywords from a vector of text using the RAKE algorithm. RAKE doesn't require any training data, so it's super easy to use:

```{r, eval = FALSE}
library(slowraker)

data("dog_pubs")
rakelist <- slowrake(txt = dog_pubs$title[1:5])
```

```{r, eval = TRUE, results = 'hide', echo = FALSE}
# Note, we have to split the README.Rmd up like this so that it doesn't print 
# out the progress bar.
library(slowraker)
options(width = 100)

data("dog_pubs")
rakelist <- slowrake(txt = dog_pubs$title[1:5])
```

`slowrake()` outputs a list of data frames, with each data frame containing the keywords that were extracted from a document:

```{r}
rakelist
```

We can bind these data frames together using `rbind_rakelist()`:

```{r}
rakedf <- rbind_rakelist(rakelist = rakelist, doc_id = dog_pubs$doi[1:5])
head(rakedf, 5)
```