---
title: "rapidraker"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{rapidraker}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  progress = FALSE,
  error = FALSE, 
  message = FALSE,
  warning = FALSE
)
options(width = 100, digits = 2)
```

## What is `rapidraker`?

`rapidraker` is an R package that provides an implementation of the same keyword extraction algorithm (RAKE) that `slowraker` does. However, `rapidraker::rapidrake()` is written mostly in Java while `slowraker::slowrake()` is written mostly in R. This means that you can expect `rapidrake()` to be considerably faster than `slowrake()`.

## Installation

You can get the stable version on CRAN:

```r
install.packages("rapidraker")
```

The development version of the package requires you to compile the latest Java source code in [rapidrake-java](https://github.com/crew102/rapidrake-java), so it's not as simple as making a call to  `devtools::install_github()`.

## Basic usage

```{r, eval = FALSE}
library(slowraker)
library(rapidraker)

data("dog_pubs")
rakelist <- rapidrake(txt = dog_pubs$abstract[1:5])
head(rbind_rakelist(rakelist))
```

```{r, echo = FALSE, results = "hide"}
# Note, we have to split the vignette up like this so that it doesn't print 
# the progress bar.
library(slowraker)
library(rapidraker)

data("dog_pubs")
rakelist <- rapidrake(txt = dog_pubs$abstract[1:5])
```

```{r, echo = FALSE}
head(rbind_rakelist(rakelist))
```

## Performance of `slowraker` vs `rapidraker`

```{r, results = 'hide'}
txt <- rep(dog_pubs$abstract, 20)

sr_time <- system.time(slowrake(txt))[["elapsed"]]
rr_time <- system.time(rapidrake(txt))[["elapsed"]]
```

In this example, `slowrake()` took `r sr_time` seconds to execute while `rapidrake()` took `r rr_time` seconds, suggesting that the Java implementation of RAKE was about `r round(sr_time / rr_time, 0)` times faster than the R version.

## Making `rapidrake()` even faster

Executing RAKE is an example of an embarrassingly parallel problem. As such, it doesn't take much code to parallelize `rapidrake()`:

```{r}
# The following simulations were run on an 8 core Windows machine
library(parallel)
library(doParallel)
library(foreach)

cores <- detectCores()
# Make txt vector larger so we can more easily see the speed improvement of 
# parallelization
txt2 <- rep(txt, cores) 
by <- floor(length(txt2) / cores)

cl <- makeCluster(cores)
registerDoParallel(cl)

rr_par_time <- system.time(
  foreach(i = 1:cores) %dopar% {
    start <- (i - 1) * by + 1
    finish <- start + by - 1
    rapidraker::rapidrake(txt2[start:finish])
  }
)[["elapsed"]]

stopCluster(cl)
```

The sequential version of `rapidrake()` took `r rr_time` seconds to extract keywords for `r length(txt)` documents, while the parallel version took `r rr_par_time` seconds to extract keywords for `r length(txt2)` documents. This suggests that the parallel version was about `r round(rr_time * cores / rr_par_time, 0)` times faster than the regular version.